---
title: "Futures"
output:
  pdf_document:
    toc: yes
    toc_depth: '2'
  html_document:
    toc: yes
    toc_depth: 2
  word_document:
    toc: yes
    toc_depth: '2'
date: "2023-02-27"
always_allow_html: yes
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Libraries

```{r message=FALSE}
library(TSstudio)
library(tidyverse)
library(quantmod)
library(zoo)
library(janitor)
library(lubridate)
library(readr)
library(timetk)
library(fpp2)         # The forecasting OG
library(fpp3)         # The tidy version of fpp2
library(modeltime)    # The tidy forecasting newcomer
library(timetk)       # Companion to modeltime
library(parsnip)      # Common interface for specifying models
library(rsample)      # Training / Test data splitter
library(cowplot) 
```
## Abstract

## Introduction



## Literature Review



## Exploratory Data Analysis

### Importing Data
```{r, message=FALSE}

BTC_futures_data <- read_csv("data/BTC futures data.csv")
BTC_historical_data <- read_csv("data/BTC historical_data.csv")
Global_Inflation <- read_csv("data/Global Dataset of Inflation.csv")
Shanghai_delayed_Index <- read_csv("data/Shanghai delayed Index.csv")
SP500_Perfomance <- read_csv("data/SP500 Perfomance.csv")
```

### Global Inflation Analysis

```{r}
df = Global_Inflation
df = df %>% clean_names()
df = filter(df, df$country_code == "USA")
df = df %>% select(-(country_code:indicator_type))
df_s  = cbind(df[1], stack(df[2:60]))
df_s$ind<-gsub("x","",as.character(df_s$ind))
df_s =  df_s %>% mutate_at(c('ind', 'values'), as.numeric)
df_s = na.omit(df_s)
df_s = as_data_frame(df_s)
# Visualization
ggplot(df_s, aes(x = ind, y = values)) + 
  geom_line(aes(color = series_name, linetype = series_name)) + theme_light()
```

#### Discussion:


```{r}
df_s = filter(df_s, ind >= 2017)
df_s = df_s %>% select(-c(series_name))
df_s = df_s %>%
  group_by(ind) %>%
  summarise_at(vars(values), list(name = mean))
```


#### Discussion:

```{r}
# grouped boxplot
ggplot(df_s, aes(x=as_factor(ind), y=name)) + 
    geom_boxplot() + theme_light()
```

#### Findings


### BTC Historical Prices Analysis

```{r}
btc = BTC_historical_data
btc = btc %>% 
    rename("timestamp" = "...1")
btc_df = btc
btc <- slice(btc, 1:(n() - 1)) 
btc$var = btc$high - btc$low
btc = select(btc, -c(open, low, high, close))
btc$timestamp = as_date(btc$timestamp)

# Lags
btc = btc %>%
    group_by(ticker) %>%
    tk_augment_lags(contains("open"), .lags = 1)
btc = na.omit(btc)
btc_df = btc
df  = zoo(btc)
```

```{r}
ggplot(data = btc, aes(x = as.POSIXct.Date(timestamp), y = adjclose)) +
  # plot the raw data
  geom_line() + theme_light() +
  labs(x = "Time", y = "Closing BTC Price in USD") +
  scale_x_datetime(date_breaks = "year", date_labels = "%b-%Y")
```
#### Discussion

```{r}
ggplot(data = btc, aes(x = as.POSIXct.Date(timestamp), y = btc$adjclose)) +
  # plot the raw data
  geom_line() +
  labs(x = "Time", y = "Closing Prices Lag 3") + theme_light() +
  scale_x_datetime(date_breaks = "year", date_labels = "%b-%Y")
```

#### Discussion

```{r}
ggplot(data = btc, aes(x = as.POSIXct.Date(timestamp), y = volume)) +
  # plot the raw data
  geom_line() +
  labs(x = "Time", y = "Volume of BTC Traded") + theme_light() +
  scale_x_datetime(date_breaks = "year", date_labels = "%b-%Y")
```

#### Exploring Seasonality/Cyclic nature of the data


```{r}
plot_stl_diagnostics(btc, .date_var = timestamp, .value = adjclose)
```


```{r}
plot_seasonal_diagnostics(btc, .date_var = timestamp, .value = adjclose)
```


```{r}
btc$month = month(btc$timestamp, label = TRUE)
btc$year = year(btc$timestamp)
btc$wk = week(btc$timestamp)
btc$wkday = as_factor(weekdays(btc$timestamp))

dfm<- 
  btc %>% 
  summarize_by_time(.date_var = timestamp,
                    .by = "month",
                    avg_adj = mean(adjclose, na.rm = TRUE),
                     avg_vol= mean(volume, na.rm = TRUE),
                    avg_var = mean(var, na.rm = TRUE))

dfm_btc = dfm

ggplot(data = dfm, aes(x = as.POSIXct.Date(timestamp) , y = avg_adj)) +
  geom_line() +
  geom_smooth(se = FALSE) +
  labs(x = "Months", y = "Adjusted Close Price") + theme_light()+
  scale_x_datetime(date_breaks = "year", date_labels = "%b-%Y")


```

```{r}
ggplot(data = dfm, aes(x = as.POSIXct.Date(timestamp) , y = avg_vol)) +
  geom_line() +
  geom_smooth(se = FALSE) +
  labs(x = "Months", y = "Adjusted Close Price") + theme_light()+
  scale_x_datetime(date_breaks = "year", date_labels = "%b-%Y")
```

```{r}
ggplot(data = dfm, aes(x = as.POSIXct.Date(timestamp) , y = avg_var)) +
  geom_line() +
  geom_smooth(se = FALSE) +
  labs(x = "Months", y = "Adjusted Difference in Price") + theme_light()+
  scale_x_datetime(date_breaks = "year", date_labels = "%b-%Y")
```


```{r}
plot_stl_diagnostics(dfm, .date_var = timestamp, .value = avg_adj)
```

```{r}
plot_seasonal_diagnostics(dfm, .date_var = timestamp, .value = avg_adj)
```




### BTC Futures Analysis

```{r}
btcf = BTC_futures_data
btcf = btcf %>% 
    rename("timestamp" = "...1")
btcf <- slice(btcf, 1:(n() - 1)) 
btcf_df = btcf
btcf$var = btcf$high - btcf$low
btcf = select(btcf, -c(open, low, high, close))
btcf$timestamp = as_date(btcf$timestamp)

# Lags
btcf = btcf %>%
    group_by(ticker) %>%
    tk_augment_lags(contains("adjclose"), .lags = 1:3)
btcf = na.omit(btcf)
df  = zoo(btcf)
```

```{r}
ggplot(data = btcf, aes(x = as.POSIXct.Date(timestamp), y = adjclose)) +
  # plot the raw data
  geom_line() +
  labs(x = "Time", y = "BTC Futures Closing Prices") + theme_light()+
  scale_x_datetime(date_breaks = "year", date_labels = "%b-%Y")

```

```{r}
ggplot(data = btcf, aes(x = as.POSIXct.Date(timestamp), y = volume)) +
  # plot the raw data
  geom_line() +
  labs(x = "Time", y = "Volume of BTC Futures Traded") + theme_light()
  scale_x_datetime(date_breaks = "year", date_labels = "%b-%Y")
```

```{r}
ggplot(data = btcf, aes(x = as.POSIXct.Date(timestamp), y = adjclose_lag3)) +
  # plot the raw data
  geom_line() +
  labs(x = "Time", y = "Closing Prices Lag 3") + theme_light()+
  scale_x_datetime(date_breaks = "year", date_labels = "%b-%Y")
```

```{r}
plot_stl_diagnostics(btcf, .date_var = timestamp, .value = adjclose)
```

```{r}
plot_seasonal_diagnostics(btcf, .date_var = timestamp, .value = adjclose)
```

```{r}
btcf$month = month(btcf$timestamp, label = TRUE)
btcf$year = year(btcf$timestamp)
btcf$wk = week(btcf$timestamp)
btcf$wkday = as_factor(weekdays(btcf$timestamp))

dfm<- 
  btcf %>% 
  summarize_by_time(.date_var = timestamp,
                    .by = "month",
                    avg_adj_f = mean(adjclose, na.rm = TRUE),
                     avg_vol_f= mean(volume, na.rm = TRUE),
                    avg_var_f = mean(var, na.rm = TRUE))

dfm_btcf = dfm

ggplot(data = dfm, aes(x = as.POSIXct.Date(timestamp) , y = avg_adj_f)) +
  geom_line() +
  geom_smooth(se = FALSE) +
  labs(x = "Months", y = "Adjusted Close Price") + theme_light()+
  scale_x_datetime(date_breaks = "year", date_labels = "%b-%Y")


```

```{r}
ggplot(data = dfm, aes(x = as.POSIXct.Date(timestamp) , y = avg_vol_f)) +
  geom_line() +
  geom_smooth(se = FALSE) +
  labs(x = "Months", y = "Adjusted Close Price") + theme_light()+
  scale_x_datetime(date_breaks = "year", date_labels = "%b-%Y")
```

```{r}
ggplot(data = dfm, aes(x = as.POSIXct.Date(timestamp) , y = avg_var_f)) +
  geom_line() +
  geom_smooth(se = FALSE) +
  labs(x = "Months", y = "Adjusted Difference in Price") + theme_light()+
  scale_x_datetime(date_breaks = "year", date_labels = "%b-%Y")
```

### SP500 Index Perfomance Analysis

```{r}
sp = SP500_Perfomance
sp = sp %>% 
    rename("timestamp" = "...1")
sp <- slice(sp, 1:(n() - 1)) 
sp_df = sp
sp$var = sp$high - sp$low
sp = select(sp, -c(open, low, high, close))
sp$timestamp = as_date(sp$timestamp)

# Lags
sp = sp %>%
    group_by(ticker) %>%
    tk_augment_lags(contains("adjclose"), .lags = 1:3)
sp = na.omit(sp)
df  = zoo(sp)
```

```{r}
ggplot(data = sp, aes(x = as.POSIXct.Date(timestamp), y = adjclose)) +
  # plot the raw data
  geom_line() +
  labs(x = "Time", y = "Closing Prices") + theme_light()+
  scale_x_datetime(date_breaks = "year", date_labels = "%b-%Y")

```

```{r}
ggplot(data = sp, aes(x = as.POSIXct.Date(timestamp), y = volume)) +
  # plot the raw data
  geom_line() +
  labs(x = "Time", y = "Volume Traded") + theme_light()+
  scale_x_datetime(date_breaks = "year", date_labels = "%b-%Y")
```

```{r}
ggplot(data = sp, aes(x = as.POSIXct.Date(timestamp), y = adjclose_lag3)) +
  # plot the raw data
  geom_line() +
  labs(x = "Time", y = "Closing Prices Lag 3") + theme_light()+
  scale_x_datetime(date_breaks = "year", date_labels = "%b-%Y")
```


```{r}
sp$month = month(sp$timestamp, label = TRUE)
sp$year = year(sp$timestamp)
sp$wk = week(sp$timestamp)
sp$wkday = as_factor(weekdays(sp$timestamp))

dfm<- 
  sp %>% 
  summarize_by_time(.date_var = timestamp,
                    .by = "month",
                    avg_adj_sp = mean(adjclose, na.rm = TRUE),
                     avg_vol_sp= mean(volume, na.rm = TRUE),
                    avg_var_sp = mean(var, na.rm = TRUE))

dfm_sp = dfm
ggplot(data = dfm, aes(x = as.POSIXct.Date(timestamp) , y = avg_adj_sp)) +
  geom_line() +
  geom_smooth(se = FALSE) +
  labs(x = "Months", y = "Adjusted Close Price") + theme_light()+
  scale_x_datetime(date_breaks = "year", date_labels = "%b-%Y")


```

```{r}
ggplot(data = dfm, aes(x = as.POSIXct.Date(timestamp) , y = avg_vol_sp)) +
  geom_line() +
  geom_smooth(se = FALSE) +
  labs(x = "Months", y = "Adjusted Close Price") + theme_light()+
  scale_x_datetime(date_breaks = "year", date_labels = "%b-%Y")
```

```{r}
ggplot(data = dfm, aes(x = as.POSIXct.Date(timestamp) , y = avg_var_sp)) +
  geom_line() +
  geom_smooth(se = FALSE) +
  labs(x = "Months", y = "Adjusted Difference in Price") + theme_light()+
  scale_x_datetime(date_breaks = "year", date_labels = "%b-%Y")
```

### Shanghai Delayed Index Perfomance Analysis

```{r}
sh = Shanghai_delayed_Index
sh <- slice(sh, 1:(n() - 1)) 
sh = sh %>% 
    rename("timestamp" = "...1")
sh <- slice(sh, 1:(n() - 1)) 
sh_df = sh
sh$var = sh$high - sh$low
sh = select(sh, -c(open, low, high, close))
sh$timestamp = as_date(sh$timestamp)

# Lags
sh = sh %>%
    group_by(ticker) %>%
    tk_augment_lags(contains("adjclose"), .lags = 1:3)
sh = na.omit(sh)
df  = zoo(sh)
```

```{r}
ggplot(data = sh, aes(x = as.POSIXct.Date(timestamp), y = adjclose)) +
  # plot the raw data
  geom_line() +
  labs(x = "Time", y = "Closing Prices") +
  scale_x_datetime(date_breaks = "year", date_labels = "%b-%Y") +theme_light()

```

```{r}
ggplot(data = sh, aes(x = as.POSIXct.Date(timestamp), y = volume)) +
  # plot the raw data
  geom_line() +
  labs(x = "Time", y = "Volume Traded") + theme_light()+
  scale_x_datetime(date_breaks = "year", date_labels = "%b-%Y")
```

```{r}
ggplot(data = sh, aes(x = as.POSIXct.Date(timestamp), y = adjclose_lag3)) +
  # plot the raw data
  geom_line() +
  labs(x = "Time", y = "Closing Prices Lag 3") + theme_light()+
  scale_x_datetime(date_breaks = "year", date_labels = "%b-%Y")
```

```{r}
plot_stl_diagnostics(sh, .date_var = timestamp, .value = adjclose)
```

```{r}
plot_seasonal_diagnostics(sh, .date_var = timestamp, .value = adjclose)
```

```{r}
sh$month = month(sh$timestamp, label = TRUE)
sh$year = year(sh$timestamp)
sh$wk = week(sh$timestamp)
sh$wkday = as_factor(weekdays(sh$timestamp))

dfm<- 
  sh %>% 
  summarize_by_time(.date_var = timestamp,
                    .by = "month",
                    avg_adj_sh = mean(adjclose, na.rm = TRUE),
                     avg_vol_sh= mean(volume, na.rm = TRUE),
                    avg_var_sh = mean(var, na.rm = TRUE))

dfm_sh = sh

ggplot(data = dfm, aes(x = as.POSIXct.Date(timestamp) , y = avg_adj_sh)) +
  geom_line() +
  geom_smooth(se = FALSE) +
  labs(x = "Months", y = "Adjusted Close Price") + theme_light()+
  scale_x_datetime(date_breaks = "year", date_labels = "%b-%Y")

```

```{r}
ggplot(data = dfm, aes(x = as.POSIXct.Date(timestamp) , y = avg_vol_sh)) +
  geom_line() +
  geom_smooth(se = FALSE) +
  labs(x = "Months", y = "Adjusted Close Price") + theme_light()+
  scale_x_datetime(date_breaks = "year", date_labels = "%b-%Y")
```

```{r}
ggplot(data = dfm, aes(x = as.POSIXct.Date(timestamp) , y = avg_var_sh)) +
  geom_line() +
  geom_smooth(se = FALSE) +
  labs(x = "Months", y = "Adjusted Difference in Price") + theme_light()+
  scale_x_datetime(date_breaks = "year", date_labels = "%b-%Y")
```

## Modeling

```{r}
library(tsibble)
library(feasts)
```


```{r}
sp_df = sp_df %>% 
  select(-c(open, high, low, close, volume, ticker,close,high)) %>%
  rename("close_sp" = "adjclose")
sh_df = sh_df %>% 
  select(-c(open, high, low, close, volume, ticker,close,high)) %>%
  rename("close_sh" = "adjclose")
btc_df = btc_df %>% select(-c(ticker, volume, var))
btcf_df  = btcf_df %>% 
  select(-c(open,high, low, close, ticker, volume))%>% 
    rename("close_f" = "adjclose")
```

```{r}
df = merge(btc_df,btcf_df,by="timestamp")
df = merge(df,sp_df,by="timestamp")
df = merge(df,sh_df,by="timestamp")
df = df %>% select(-c(ticker))
df$timestamp = as.POSIXct.Date(df$timestamp)
```


```{r}
df = merge(btc_df,btcf_df,by="timestamp")
df = merge(df,sh_df,by="timestamp")
df = merge(df,sp_df,by="timestamp")
df$month = month(df$timestamp, label = TRUE)
df$year = year(df$timestamp)
df$wk = week(df$timestamp)
df$wkday = as_factor(weekdays(df$timestamp))
df = select(df, -ticker)
```


##### Time Series Plots

```{r}
df |>
  mutate(timestamp = ymd(timestamp)) |>
  as_tsibble(index = timestamp) |> group_by_key() %>% fill_gaps()-> df_ts


autoplot(df_ts, close_f) +
  labs(title = "Closing Prices For Futures",
       subtitle = "BTC Futures",
        y = "Closing Price") + theme_light()
```


```{r}
df_ts |>
  gg_season(close_f, labels = "both") +
  labs(y = "Closing Prices",
       title = "Seasonal plot: BTC Futures Prices") + theme_light()
```

```{r}
df_ts |>
  autoplot(close_sh) +
  labs(
    y = "Closing Price",
    title = "Shanghai Delayed Index"
  ) +theme_light()
```
##### Scatter Plots

```{r}
df_ts  |>
  ggplot(aes(x = close_sp, y = close_f)) +
  geom_point() + geom_smooth()+
  labs(x = "Closing Prices of SP500",
       y = "Closing Prices BTC Futures)") +theme_light()
```

```{r}
df_ts  |>
  ggplot(aes(x = close_sh, y = close_f)) +
  geom_point() + geom_smooth()+
  labs(x = "Closing Prices of Shanghai Delayed Index",
       y = "Closing Prices BTC Futures)") +theme_light()
```
### Correlation

```{r}
df_ts |> GGally::ggpairs(columns = 2:5)
```
## Lag Plots

```{r}
recent_prices <- df_ts |>
  filter(year(timestamp) >= 2018)
recent_prices |>
  gg_lag(adjclose, geom = "point") +
  labs(x = "lag(Closing Price For BTC, k)")
```
### AutoCorrelation

```{r}
df_ts |> ACF(close_f, lag_max = 4)
```


```{r}
recent_prices |>
  ACF(close_f, lag_max = 4) |>
  autoplot() + labs(title="Closing Prices For BTC Futures") + theme_light()
```
```{r}
df_ts |>
  autoplot(close_f/adjclose) +
  labs(title= "Future Price Per BTC Price", y = "$US") +theme_light()
```

```{r}
df_ts |>
  autoplot(close_f/close_sp) +
  labs(title= "Future Price Against SP500", y = "$US") +theme_light()
```

```{r}
lambda <- df_ts |>
  features(close_f, features = guerrero) |>
  pull(lambda_guerrero)
df_ts |>
  autoplot(box_cox(close_f, lambda)) +
  labs(y = "",
       title = latex2exp::TeX(paste0(
         "Transformed gas production with $\\lambda$ = ",
         round(lambda,2)))) +theme_light()
```
### Decomposing Time Series

```{r}
df_ts <- df_ts |>
  mutate(
    `4-MA` = slider::slide_dbl(close_f, mean,
                .before = 1, .after = 2, .complete = TRUE)
  )



df_ts |>
  autoplot(close_f) +
  geom_line(aes(y = `4-MA`), colour = "green") +
  labs(y = "Price",
       title = "BTC Futures Prices") +
  guides(colour = guide_legend(title = "series")) +theme_light()
```
```{r}
# 1. Plot the data and identify any unusual observations.
df_ts %>%
  plot_time_series(
    .date_var = timestamp,
    .value = close_f,
    .smooth_alpha = 0.6,
    .interactive = FALSE,
    .title = "The BTC Futures Trend"
  )
```



```{r}
# 3. Automatically fit multiple models and find the lowest AICc.
library(tidymodels)
# Split the data 80/20 
splits <- rsample::initial_time_split(df_ts, prop = 0.8)
# Model Spec
model_spec_arima <- arima_reg() %>%
  set_engine("auto_arima")
# Fit Spec
model_fit_arima <- model_spec_arima %>%
  fit(close_f ~ timestamp + close_sp + close_sh, data = rsample::training(splits))

# Fit Spec
model_fit_arima2 <- model_spec_arima %>%
  fit(close_f ~ timestamp, data = rsample::training(splits))
# Check model report
model_fit_arima2
```
```{r}
modeltime_table(model_fit_arima2)
```


```{r}
# Create table of model to use
auto_arima_model_tbl <- modeltime_table(model_fit_arima2)
# Calibrate the model to produce confidence intervals
arima_calibration_tbl <- auto_arima_model_tbl %>%
  modeltime_calibrate(new_data = rsample::testing(splits), quiet = FALSE)
# Create residuals table
arima_residuals_tbl <- arima_calibration_tbl %>% modeltime_residuals()
# Plot the residuals
u1 <- arima_residuals_tbl %>% 
  plot_modeltime_residuals(
    .type = "timeplot", 
    .interactive = FALSE)
u2 <- arima_residuals_tbl %>% 
  plot_modeltime_residuals(
    .type = "acf", 
    .interactive = FALSE,
    .title = "ACF and PACF Plots")
# Check for white noise with a Ljung-Box test
arima_residuals_tbl %>%
  select(.residuals, .index) %>%
  as_tsibble() %>%  # fabletools workaround
  features(.residuals, ljung_box, lag=24, dof=0)
# Arrange plots
plot_grid(u1, u2, ncol=1)
```



```{r}
total = merge(total,dfm_sh,by="timestamp")
total = merge(total,dfm_btcf,by="timestamp")
total <- total %>% select(-contains("ticker"))
# binding data frames
total$infl = total$year
total$infl[total$year == 2017] = 2.858
total$infl[total$year == 2018] = 6.896
total$infl[total$year == 2019] = 5.570
total$infl[total$year == 2020] = 1.382
total$infl[total$year == 2021] = 8.340
total$infl[total$year == 2022] = 12.120
total$infl[total$year == 2023] = NA
```


```{r}
library(rsample)
df_split <- initial_time_split(total, prop = 150/156)

df_training <- training(df_split)
df_testing <- testing(df_split)


forecast_1 <- lm(avg_adj ~., data = df_training)
broom::tidy(forecast_1)
```

